---
title: "In Class Exercise 4"
description: |
  A new article created using the Distill format.
author:
  - name: Sean Samuel Prajs 
    url: https://github.com/SeanP0110
    affiliation: SMU
date: "`r Sys.Date()`"
output: distill::distill_article
---


# ggstatsplot

```{r, eval=TRUE, echo=TRUE}
packages = c('ggstatsplot', 'ggside', 'tidyverse')
#install.packages('PMCMRplus') #for pairwise comparison
#install devtools

for(p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p, character.only = T)
}

#ggside: used to create side by side plots like 
#scatterplot with side boxplot

exam <- read.csv("data/Exam_data.csv")


#One-sample test
set.seed(1234)

gghistostats(
  data = exam,
  x = ENGLISH,
  type = "bayes",
  test.value = 60,
  xlab ="English scores"
)


#two-sample mean test
ggbetweenstats(
  data = exam,
  x = GENDER,
  y = MATHS,
  type = "np",
  messages = FALSE
)

ggbetweenstats(
  data = exam,
  x = RACE,
  y = ENGLISH,
  type ="p",
  mean.ci =TRUE,
  pairwise.comparisons =TRUE,
  pairwise.display ="s",
  p.adjust.method ="fdr",
  messages = FALSE
)

ggscatterstats(
  data = exam,
  x = MATHS,
  y = ENGLISH,
  marginal = TRUE,
)


exam1 <- exam %>%
  mutate(MATHS_bins =
           cut(MATHS,
               breaks = c(0,60,75,85,100))
  )

ggbarstats(exam1,
           x = MATHS_bins,
           y = GENDER)
```

# Toyota Case Study

## package loading

```{r, eval=TRUE, echo=TRUE}
packages = c('readxl','report','performance','parameters','see')

for(p in packages){
  if(!require(p,character.only=T)){
    install.packages(p)
  }
  library(p, character.only =T)
  }
```

## data loading and preparation

```{r, eval=TRUE,echo=TRUE}
car_resale <- read_xls("data/ToyotaCorolla.xls","data")

model <- lm(Price ~ Age_08_04 + Mfg_Year + KM +
              Weight + Guarantee_Period, data = car_resale)
model
```

## Model Diagnostic

### Checking for multicollinearity

```{r, eval=TRUE, echo=TRUE}
check_collinearity(model) #from performance library

check_c <- check_collinearity(model)
plot(check_c) #this is from the see library
```

### checking the normality assumption

```{r, eval=TRUE, echo=TRUE}
check_n <- check_normality(model)
plot(check_n)
```

### checking the homogeneity

```{r, eval=TRUE, echo=TRUE}
check_h <- check_heteroscedasticity(model)
plot(check_h)
```

### complete check

```{r, eval=TRUE, echo=TRUE}
check_model(model)
```

## Visual Regression Paramaters:

```{r, eval=TRUE, echo=TRUE}
plot(parameters(model))

ggcoefstats(model, output = "plot")
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Distill is a publication format for scientific and technical writing, native to the web. 

Learn more about using Distill for R Markdown at <https://rstudio.github.io/distill>.





